I am a title (RO SLAM Methods/Implementation Survey)

### 2018-01-19 Paper.tex
latest particle filter complete

\documentclass[conference]{IEEEtran}
\usepackage{graphicx}
\usepackage{placeins}
\graphicspath{{Figures/}}

\begin{document}
	\title{I am a title (RO SLAM Methods/Implementation Survey) }

@@

\section{range only sensors/tech}
\section{Methods...}
\subsection{EKF}
%breif description (1-2 paragraphs)
%paragraphs 
The Extended Kalman Filter (EKF) is one of the most popular and widespread methods used to solve the SLAM problem. It is used to overcome the assumption of linear state transitions and measurements, which are rarely seen in practical environments \cite{Thrun2002}. The derivation of the EKF is very well documented, as such, detailed explanations can be viewed from a variety of sources such as: \cite{Thrun2002}, \cite{Ribeiro2004}, and \cite{Haykin2001}. When used to solve SLAM the map applied to the EKF is a feature based map, meaning it is composed of observable features (landmarks) which can be distinguished between during re-observation \cite{Thrun2002}. This distinction becomes important when examining range only SLAM (RO-SLAM) where only the range to a landmark, or the range between landmarks, is known. This restriction means that landmarks often need to be manufactured, such as those discussed in section II, and physically placed in an environment. However, that does not mean that the exact location of the landmarks, or even there initial existence, is recognized. Initialization is a critical element in many algorithms that make use of the EKF. If the initialization is inaccurate then the convergence to a correct estimation becomes much more difficult for the filter. The EKF has seen a wide variety of implementation ranging from ground based robotics\cite{Djugash2008}, to unmanned air vehicles \cite{Fabresse2016}, and to autonomous underwater vehicles \cite{Olson2006}. This section will proceed to give a summary of the various ways EKF has been implemented in regards to RO SLAM, as well as examine improvements to the general RO SLAM problem that are applied via EKF.

@@

%fabreese. 
%1. 2013 presents EKF slam method for ariel vehicles 
%2. 2014 introduces prefiltering to measurments for previous 
%3. 2014a integrates visual landmakrs as well
%4  2015 decentralized multiple arieal vehicles
%5  2016 specifically unmaned ariel, more details on 2013,2014 and experimental validation of 2013,2014.

@@

Several techniques have also been implemented that involve cooperative sensors. Traditionally sensors were used to only determine the range between themselves and the robot. The sensors in these cases provide the ability determine the range between themselves and other sensors and or the robot \cite{Patwari2005}.
\begin{figure}[h!]
	\centering
	\includegraphics[width=90mm]{coop_loc_comp_patwari.png}
	\caption{Traditional(a) vs Cooperative(b) Sensors \cite{Patwari2005}}
	\label{trad_vs_coop_sensors}
\end{figure}
\FloatBarrier

@@

An extension to EKF called relative-over parametrized (ROP) EKF is presented by \cite{Djugash2008}. This extension uses specific parameterization to  better represent the range only data utilized in RO-SLAM. ROP EKF operates in polar coordinates as opposed to the Cartesian space that typical EKF operates. The method provided improved results over EKF when sparse range measurement of data association errors were present. \cite{Herranz2014} presents a comparison of the ROP-EKF method presented by \cite{Djugash2008}e{Djugash2008},to a smoothing and mapping method presented by \cite{Dellaert2006}. Experimentation conducted by Herranz on and indoor and outdoor environment show an improvement in the results of the SAM method over ROP EKF.
\begin{figure}[h!]
	\centering
	\includegraphics[width=90mm]{ROP_djugash.png}
	\caption{True and approximated distributions with one range observation (Top Row) and two observations from different locations (Bottom Row). True distributions in	Cartesian coordinates (Left Column), true and Gaussian approximated distributions in polar coordinates (Middle Column), and projection of the Gaussian approximated. \cite{Djugash2008}} LITERALLY COPIED, CHANGE DIS?%THIS WAS LITTERALY COPYIED AND PASTED AND NEEDS TO BE CHANGED AT SOME POINTS
	\label{ROP_djugash}
\end{figure}
\FloatBarrier

A method proposed by \cite{Dios2015} is geared towards improving map building speed and accuracy for UAS dealing with the 3D RO-SLAM problem. The 3D RO-SLAM problem refers to the added complexity that devices such as submersibles \cite{Newman} and aerial vehicles experience when having to operate in an environment where three dimensions must be considered as opposed to the planar environment many robots are assumed to operate in. The method utilizes inter-beacon measurements and a novel mode selection which is used to select a measurement gathering method based on current conditions \cite{Dios2015}. The first mode is noted as mapping (MS) and the second localization (LS). When in mapping mode the measurment are integrated with a high probability to quickly create a map, when in localization mode the probability is lowered to create higher accuracy localizations. Based on experimentation performed by \cite{Dios2015} the method performed well an a general increase in accuracy and map speed was noted, however it is stated that a wider variety of experimentation should be performed to validate the overall robustness and effectiveness of the method.
	%this one might need some more work

@@

\subsection{Graph SLAM}
\subsection{Particle}
Particles filters are made ue up various monte carlo algorithms that are used to estimate states in partially observable Markov chains(see[9]). In the initial application of particle filters in the field of robotics was in localization where it was used to estimate a robots pose from sensor data. It is considered better and more robost to conventional estimtion methods because it was able to solve the global localization[2] and the kidnapped robot problem[14].It has also been at the corre higher dimentional problems  
%Description
Initially robot assumes global uncertainity through a set of particles that are distributed all over the map. Hence both the robot and the landmarks are uncertain.As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one. There are several resampling methods depending on computational complexities. After some iterations only the particles which have a high degree of probability  reamain and eventually converge to the state of the robot and the landmarks
Assuming at time t=0;we have N particles equally space in the enviornment that are drawn based on a uniform distribution p($x_o$).
Once the robot starts moving it collects measurements and at time t$>$0 we sample a new particle set $x^[i]_t$ for each partile in $(x^[i])_(t-1)$

\subsection{Graph}
\subsection{Fast SLAM}
%Brief introduction

%advantages
%Disadvantages

@@

	\bibliographystyle{IEEEtran}
	\bibliography{references}

>>>>

\documentclass[conference]{IEEEtran}

\usepackage{graphicx}

\usepackage{placeins}

\graphicspath{{Figures/}}

\begin{document}

	\title{I am a title (RO SLAM Methods/Implementation Survey) }

@@

	\section{range only sensors/tech}

	\section{Methods...}

	\subsection{EKF}

	%breif description (1-2 paragraphs)

	%paragraphs

	The Extended Kalman Filter (EKF) is one of the most popular and widespread methods used to solve the SLAM problem. It is used to overcome the assumption of linear state transitions and measurements, which are rarely seen in practical environments \cite{Thrun2002}. The derivation of the EKF is very well documented, as such, detailed explanations can be viewed from a variety of sources such as: \cite{Thrun2002}, \cite{Ribeiro2004}, and \cite{Haykin2001}. When used to solve SLAM the map applied to the EKF is a feature based map, meaning it is composed of observable features (landmarks) which can be distinguished between during re-observation \cite{Thrun2002}. This distinction becomes important when examining range only SLAM (RO-SLAM) where only the range to a landmark, or the range between landmarks, is known. This restriction means that landmarks often need to be manufactured, such as those discussed in section II, and physically placed in an environment. However, that does not mean that the exact location of the landmarks, or even there initial existence, is recognized. Initialization is a critical element in many algorithms that make use of the EKF. If the initialization is inaccurate then the convergence to a correct estimation becomes much more difficult for the filter. The EKF has seen a wide variety of implementation ranging from ground based robotics\cite{Djugash2008}, to unmanned air vehicles \cite{Fabresse2016}, and to autonomous underwater vehicles \cite{Olson2006}. This section will proceed to give a summary of the various ways EKF has been implemented in regards to RO SLAM, as well as examine improvements to the general RO SLAM problem that are applied via EKF.

@@

	%fabreese.

	%1. 2013 presents EKF slam method for ariel vehicles

	%2. 2014 introduces prefiltering to measurments for previous

	%3. 2014a integrates visual landmakrs as well

	%4  2015 decentralized multiple arieal vehicles

	%5  2016 specifically unmaned ariel, more details on 2013,2014 and experimental validation of 2013,2014.

@@

	Several techniques have also been implemented that involve cooperative sensors. Traditionally sensors were used to only determine the range between themselves and the robot. The sensors in these cases provide the ability determine the range between themselves and other sensors and or the robot \cite{Patwari2005}.

	\begin{figure}[h!]

		\centering

		\includegraphics[width=90mm]{coop_loc_comp_patwari.png}

		\caption{Traditional(a) vs Cooperative(b) Sensors \cite{Patwari2005}}

		\label{trad_vs_coop_sensors}

	\end{figure}

	\FloatBarrier

@@

	An extension to EKF called relative-over parametrized (ROP) EKF is presented by \cite{Djugash2008}. This extension uses specific parameterization to  better represent the range only data utilized in RO-SLAM. ROP EKF operates in polar coordinates as opposed to the Cartesian space that typical EKF operates. The method provided improved results over EKF when sparse range measurement of data association errors were present. \cite{Herranz2014} presents a comparison of the ROP-EKF method presented by \cite{Djugash2008}e{Djugash2008},to a smoothing and mapping method presented by \cite{Dellaert2006}. Experimentation conducted by Herranz on and indoor and outdoor environment show an improvement in the results of the SAM method over ROP EKF.

	\begin{figure}[h!]

		\centering

		\includegraphics[width=90mm]{ROP_djugash.png}

		\caption{True and approximated distributions with one range observation (Top Row) and two observations from different locations (Bottom Row). True distributions in	Cartesian coordinates (Left Column), true and Gaussian approximated distributions in polar coordinates (Middle Column), and projection of the Gaussian approximated. \cite{Djugash2008}} LITERALLY COPIED, CHANGE DIS?%THIS WAS LITTERALY COPYIED AND PASTED AND NEEDS TO BE CHANGED AT SOME POINTS

		\label{ROP_djugash}

	\end{figure}

	\FloatBarrier

	A method proposed by \cite{Dios2015} is geared towards improving map building speed and accuracy for UAS dealing with the 3D RO-SLAM problem. The 3D RO-SLAM problem refers to the added complexity that devices such as submersibles \cite{Newman} and aerial vehicles experience when having to operate in an environment where three dimensions must be considered as opposed to the planar environment many robots are assumed to operate in. The method utilizes inter-beacon measurements and a novel mode selection which is used to select a measurement gathering method based on current conditions \cite{Dios2015}. The first mode is noted as mapping (MS) and the second localization (LS). When in mapping mode the measurment are integrated with a high probability to quickly create a map, when in localization mode the probability is lowered to create higher accuracy localizations. Based on experimentation performed by \cite{Dios2015} the method performed well an a general increase in accuracy and map speed was noted, however it is stated that a wider variety of experimentation should be performed to validate the overall robustness and effectiveness of the method.

	%this one might need some more work

@@

	\subsection{Graph SLAM}

\subsection{Particle}      %change the references
Particles filters are made ue up various monte carlo algorithms that are used to estimate states in partially observable Markov chains(see[9]). In the initial application of particle filters in the field of robotics was in localization where it was used to estimate a robots pose from sensor data. It is considered better and more robust to conventional estimation methods because it was able to solve the global localization[2] and the kidnapped robot problem[14].It has also been at the corre higher dimensional problems  
%Description
Initially robot assumes global uncertainity through a set of particles that are distributed all over the map. Hence both the robot and the landmarks are uncertain.As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one. There are several resampling methods depending on computational complexities. After some iterations only the particles which have a high degree of probability  reamain and eventually converge to the state of the robot and the landmarks.
\begin{figure}[h!]
	\centering
	\includegraphics[height=40mm,width=90mm]{Particle_filter_method.JPG}
	\caption{The leftmost image describes the state of the robot when it just initializes the particle filter. The particles are uniformly distributed.The image in the center describes the particle filter after a couple of iterations. Only the particles which have a higher probability are re sampled. The image on the right shows the particle filter eventually converging to estimate the robot location. }

\end{figure}
Assuming at time t=0;we have N particles equally space in the enviornment that are drawn based on a uniform distribution $ p(x_oa)$.                                                                        resampling methods depending on computational complexities. After some iterations only th   p
Once the robot starts moving it collects measurements and at time $t>0$ we sample a new particle set $x^{[i]}_t$ for each particle in $x^{[i]}_{(t-1)}$. It is sampled based on the probability of measurement $p(z_t|x^{[i]}_{(t-1)})$. Eventually the particle filter converges to give us the true positioning of the robot.

As mentioned in[thrun particle] particle filters outperform EKF in applications involving global localization (the kidnapped robot problem form[14]) where the robot is randomly picked up and placed in a unknown environment. 
EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information[thusn book[]
As the number of particles increases the computational complexity of the filter too increases. In order to address this there were several new methods introduced that  exploit the independence among state variables. For example the Rao-Blackwellized particle filters that exploit the independence of the landmarks with the robot path thereby reducing the computation complexity. from [Fast slam paper]. It also solves the data association problem previously unsolved by EKF.[8]

	\subsection{Graph}

	\subsection{Fast SLAM}

	%Brief introduction

	%advantages

	%Disadvantages

@@

	\bibliographystyle{IEEEtran}

	\bibliography{references}
